A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss From Powdery Mildew in Australian Mungbean

### 2020-08-04 paper/paper.Rmd
Wordsmithing the introduction up to Materials and Methods

While the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.
The disease cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
<!-- couldn't we just pull this information on temperatures and RH from our data sets rather than rely on an unofficially-peer reviewed GRDC update paper? A simple figure or two could be useful here, based on our data. -->

@@

There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Australian mungbean.
Much of the experimental work has been published by funding agencies and state government extension departments as extension bulletins or other related type materials.
Past field trials in eastern Australia have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
Early trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later, if necessary, was the most effective [@SueThompson2016; @Sparks2017]. 
However, due to the variability in the results between seasons and experiments, few of these studies produced a clear result based on a statistical analysis. 
This variability presents uncertainty for the best practice of fungicide spray schedules to mitigate yield losses from powdery mildew.

@@

Considering the recent launch in November 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.

>>>>

While the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.
The disease cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].

@@

There is a near complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in mungbean in Australia.
Much of the experimental work has been published by funding agencies and state government extension departments as extension bulletins or other related type materials.
Field trials conducted in eastern Australia over the past ten years have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
The trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later, if necessary, was the most effective [@SueThompson2016; @Sparks2017].
However, due to the variability in the results between seasons and experiments, few of these studies produced a clear result based on a statistical analysis. 
This variability presents uncertainty for the best practice of fungicide spray schedules to mitigate yield losses from powdery mildew.

@@

Considering the recent launch in November 2019 of the mobile app decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
